\documentclass{ctexart}
%\usepackage{xeCJK}
%\usepackage[T1]{fontenc}
%\usepackage{mathptmx}
\usepackage{amsmath,amssymb,amsthm,color,mathrsfs}
\usepackage{enumitem,anysize}
\usepackage{geometry}
\usepackage{lipsum}
\usepackage{tikz}
\usepackage{hyperref}
\usepackage{color}
\usepackage{cleveref}
\hypersetup{
hypertex=true,
colorlinks=true,
linkcolor=red,
filecolor=blue,
urlcolor=blue,
citecolor=cyan,
}

\geometry{a4paper,left=1cm,right=1cm,top=1cm,bottom=1cm}

\def\<{\langle}
\def\>{\rangle}
\edef\lim{\displaystyle\lim}
\def\email#1{\href{mailto:#1}{\texttt{#1}}}

\newcounter{problem}
\renewcommand{\theproblem}{\Roman{problem}}
\newenvironment{problem}{\refstepcounter{problem}\noindent\color{blue}\textbf{Problem}\theproblem.}{}
\newenvironment{solution}{\begin{proof}[\textbf{Solution}]}{\end{proof}}
\crefname{problem}{Problem}{Problem}
\newcommand\Deo{\Delta_0}
\newcommand\Lo{\mathcal {L}_0}
\newcommand\N{\mathbb {N}}
\renewcommand\phi{\varphi}
\renewcommand{\(}{\left(}
\renewcommand{\)}{\right)}
\newcommand\qie{\wedge}
\newcommand\huo{\vee}
\newcommand{\bigqie}{\bigwedge}
\newcommand{\bighuo}{\bigvee}
\newcommand\calF{\mathcal{F}}
\newcommand\calA{\mathcal{A}}
\newcommand\calP{\mathscr{P}}
\newcommand{\Cb}[2]{\binom{#1}{#2}}
\newcommand{\minus}{\mathbin{\backslash}}
\newcommand{\Iff}{\Leftrightarrow}
\newcommand{\id}{\mathrm{id}}

\newtheorem{lemma}{Lemma}
\newtheorem{cora}{Corallary}
\pagestyle{empty}
\title{$\mathbb{COMBINATION}\text{2}$}
\author{王胤雅\\
SID:201911010205\\
\email{201911010205@mail.bnu.edu.cn}}



\begin{document}
\maketitle
\begin{problem}
Caculate integral between $1-1000$ which is neither square number nor cubic number.
\end{problem}

\begin{problem}
Caculate the permtation of $\{1,2,3,4,5,6\}$ $i_1i_2i_3i_4i_5i_6$, where $i_1\neq1,5$, $i_2\neq 2,3,5,$, $i_4\neq4$, $i_5\neq 5,6$.
\end{problem}


\begin{problem}
Put $n$ different balls into different $k$ boxes, none of boxes is empty. Caculate the different ways.
\end{problem}

\begin{problem}
Caculate the prime between $1-120$.
\end{problem}
\begin{problem}
There are $n$ kinds different balls, each kind of ball has $2$. Arrange these $2n$ balls into a circle, same balls are not adjacent. Caculate the different arrangement.
\end{problem}

\begin{problem}
Arrange $\{4\cdot x, 3\cdot y, 2\cdot z\}$, none of $xxxx, yyy, zz$ appears. How many  of these arrangement?
\end{problem}

\begin{problem}
Pick $10$ number from $\{\infty\cdot a,3\cdot b,5\cdot c,7\cdot d\}$, how many ways can you find?
\end{problem}

\begin{problem}
Caculate the postive integral solution of equation $x_1+x_2+x_3=14$, where $x_i\leq 8, i=1,2,3$.
\end{problem}
\iffalse
\begin{problem}
Caculate $\mu(20),\mu(105), \mu(210),$.
\end{problem}

\begin{problem}
Caculate the arithmetic function defined by $\sum_{d|n}g(d)=5$
\end{problem}
\fi


